Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-10 preliminaries.tex
Updates from Overleaf

The phase gate and Pauli matrices are denoted as follows.

@@

\begin{definition}
	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
	\begin{itemize}
		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
		\item Let $(d, z)\leftarrow(P, V)(x)$. Then $d=rej$ with probability at most $c(\lambda)$.
		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.
			Define $z_{ideal}$ by
			$$\begin{cases}
				z_{ideal}=\bot & \text{if } d=\Acc\\
				z_{ideal}\leftarrow D_x & \text{if } d=\Rej
			\end{cases}$$
			then $\norm{(d, z) - (d, z_{ideal})} \leq \varepsilon$ \Ethan{make stat. distance notation consistent}.
	\end{itemize} \hannote{need computational?} \Ethan{The norm at the end? Nah it's statistical distance}
\end{definition}

>>>>

The phase gate and Pauli matrices are the following matrices.

@@

\begin{definition}
	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
	\begin{itemize}
		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
		\item Let $(d, z)\leftarrow(P, V)(x)$. Then $d=rej$ with probability at most $c(\lambda)$.
		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.
			Define $z_{ideal}$ by
			$$\begin{cases}
				z_{ideal}=\bot & \text{if } d=\Acc\\
				z_{ideal}\leftarrow D_x & \text{if } d=\Rej
			\end{cases}$$\hannote{swap rej and acc}
			then $\norm{(d, z) - (d, z_{ideal})} \leq \varepsilon$ \Ethan{make stat. distance notation consistent}.
	\end{itemize} \hannote{need computational version of soundness?} \Ethan{The norm at the end? Nah it's statistical distance}
\end{definition}
